Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-07-29 paper.qmd
Fixed the isse with hexagon grid of Figure 3 and 7

sc_ltr_pos <- c(0.08, 0.93)
# sc_xlims <- c(-0.5, 1.47)
# sc_ylims <- c(-0.32, 2.1)
sc_xlims <- c(-0.25, 1.25)
sc_ylims <- c(-0.2, 2)

@@

hex_grid_coloured_scurve1 <- ggplot() + 
  geom_polygon(
    data = hex_grid_with_counts_s_curve1, 
    aes(x = x, y = y,
      group = hex_poly_id, 
      fill = std_counts), color = "grey70", linewidth=0.2) +
  geom_point(data = umap_scurve_scaled,
             aes(x = UMAP1, y = UMAP2),
             alpha = 0.3,
             size = 0.5) +
  scale_fill_viridis_c(direction = -1, 
    na.value = "#ffffff", option = "C") +
  interior_annotation("a", position = c(0.92, 0.93)) +
  xlim(c(-0.25, 1.35)) + ylim(c(-0.25, 2))
```

@@

hex_grid_coloured_scurve2 <- ggplot() + 
  geom_polygon(
    data = hex_grid_with_counts_s_curve2, 
    aes(x = x, y = y, 
        group = hex_poly_id, 
        fill = std_counts), 
        color = "grey70", 
        linewidth=0.2) +
  geom_point(data = umap_scurve_scaled,
           aes(x = UMAP1, y = UMAP2),
           alpha = 0.3,
           size = 0.5) +
  scale_fill_viridis_c(direction = -1, 
    na.value = "#ffffff", option = "C") +
  xlim(c(-0.25, 1.35)) + ylim(c(-0.25, 2)) +
  interior_annotation("b")

@@

hex_grid_coloured_scurve3 <-  ggplot() + 
  geom_polygon(
    data = hex_grid_with_counts_s_curve3, 
    aes(x = x, y = y, 
        group = hex_poly_id, 
        fill = std_counts), 
        color = "grey70", linewidth=0.2) +
  geom_point(data = umap_scurve_scaled,
           aes(x = UMAP1, y = UMAP2),
           alpha = 0.3,
           size = 0.5) +
  scale_fill_viridis_c(direction = -1, na.value = "#ffffff", option = "C") +
  xlim(c(-0.25, 1.35)) + ylim(c(-0.25, 2)) +
  interior_annotation("c")

>>>>

sc_ltr_pos <- c(0.08, 0.93)
# sc_xlims <- c(-0.5, 1.47)
# sc_ylims <- c(-0.32, 2.1)
sc_xlims <- c(-0.25, 1.25)
sc_ylims <- c(-0.3, 2)

@@

hex_grid_coloured_scurve1 <- ggplot() + 
  geom_polygon(
    data = hex_grid_with_counts_s_curve1, 
    aes(x = x, y = y,
      group = hex_poly_id, 
      fill = std_counts), color = "grey70", linewidth=0.2) +
  geom_point(data = umap_scurve_scaled,
             aes(x = UMAP1, y = UMAP2),
             alpha = 0.3,
             size = 0.5) +
  scale_fill_viridis_c(direction = -1, 
    na.value = "#ffffff", option = "C") +
  interior_annotation("a", position = c(0.92, 0.93)) +
  xlim(c(-0.25, 1.35)) + ylim(c(-0.35, 2))
```

@@

hex_grid_coloured_scurve2 <- ggplot() + 
  geom_polygon(
    data = hex_grid_with_counts_s_curve2, 
    aes(x = x, y = y, 
        group = hex_poly_id, 
        fill = std_counts), 
        color = "grey70", 
        linewidth=0.2) +
  geom_point(data = umap_scurve_scaled,
           aes(x = UMAP1, y = UMAP2),
           alpha = 0.3,
           size = 0.5) +
  scale_fill_viridis_c(direction = -1, 
    na.value = "#ffffff", option = "C") +
  xlim(c(-0.25, 1.35)) + ylim(c(-0.35, 2)) +
  interior_annotation("b")

@@

hex_grid_coloured_scurve3 <-  ggplot() + 
  geom_polygon(
    data = hex_grid_with_counts_s_curve3, 
    aes(x = x, y = y, 
        group = hex_poly_id, 
        fill = std_counts), 
        color = "grey70", linewidth=0.2) +
  geom_point(data = umap_scurve_scaled,
           aes(x = UMAP1, y = UMAP2),
           alpha = 0.3,
           size = 0.5) +
  scale_fill_viridis_c(direction = -1, na.value = "#ffffff", option = "C") +
  xlim(c(-0.25, 1.35)) + ylim(c(-0.35, 2)) +
  interior_annotation("c")
